---
title: "p8105_hw1_hlz2108"
output: github_document
---

This is my solution to HW1.
```{r Library}
library(tidyverse)
```


## Problem 1
The data chunk below creates a data frame comprised of:
* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", " mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r }
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor.


This code chunk applies the _as.numeric_ function to the logical, character, and factor variables.
```{r }
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric((pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
as.factor((pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)

```

## Problem 2
data("penguins", package = "palmerpenguins")

The variables in the dataset are `r v`.?
The number of rows in the dataset is `r nrow`.
The number of columns in the dataset is `r ncol`.
The mean flipper length is `r mean(flipper_length_mm)`.

