---
title: "p8105_hw1_hlz2108"
output: github_document
---

This is my solution to HW1.
```{r Library, echo = FALSE, message = FALSE}
library(tidyverse)
```

## Problem 1
The data chunk below creates a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r create_df}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", " mod", "high", "high", "high"))
  )
```

Taking the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor.


This code chunk below applies the _as.numeric_ function to the logical, character, and factor variables.
```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r multiple_numeric}
as.numeric((pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
as.factor((pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

## Problem 2
```{r load_penguin}
data("penguins", package = "palmerpenguins")
```

The Penguin dataset contains the following variables: `r ls(penguins)`.

The dataset contains the following structure: `r str(penguins)`

The number of rows in the Penguin dataset is `r nrow(penguins)`.

The number of columns in the Penguin dataset is `r ncol(penguins)`.

The mean flipper length in mm is `r mean((pull(penguins, flipper_length_mm)), na.rm=TRUE)`.

```{r scatterplot_penguin}
ggplot(penguins, aes (x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() 
ggsave("scatterplot_penguin.pdf")
```


